Geospatial - Assignment 3

### 2025-02-13 hw3/hw3_MoritzPeistNoemiLucchiSimonVellin.Rmd
updating .rmd for plot 1 - part 2

---
title: "Geospatial - Assignment 3"
author:
- Moritz Peist
- Noemi Lucchi
- Simon Vellin
output:
  html_document:
    toc: true
    df_print: paged
  pdf_document:
    toc: true
  html_notebook:
    toc: true
---

@@

```{r}
# Load populated cities and roads
places <- st_read("/hw3/data/ne_10m_populated_places")
roads <- st_read("/hw3/data/ne_10m_roads")
```

>>>>

---
title: "Geospatial - Assignment 3"
author:
- Moritz Peist
- Noemi Lucchi
- Simon Vellin
output:
  html_notebook:
    toc: true
  pdf_document:
    toc: true
  html_document:
    toc: true
    df_print: paged
---

@@

```{r}
# Load populated cities and roads
places <- st_read("/hw3/data/ex2/ne_10m_populated_places")
roads <- st_read("/hw3/data/ex2/ne_10m_roads")
```
